---
title: "Student_data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Loading survey data

```{r}
student_data <- read_csv("../data/PG_Student_data_tidy.csv")
```

Need to tidy the data a bit
```{r}
# pull out the first row which was actually the question

questions <- student_data %>% slice(1)
student_data_mod <- student_data %>% slice(-1)

# add in a respondant id column to the data which will come in useful for some later operations
student_data_mod <- student_data_mod %>% rownames_to_column(var = 'respondant')
```


Work out the appropriate divisions for the the free text responses in Q1_5 and recode them
```{r}
# the following command will let you know what the different responses were from within th column
# table(student_data_mod$Q1_5_TEXT)

# take specific entries in the Q1_5_TEXT column and convert them to the appropriate divison
student_data_mod <- student_data_mod %>% mutate(
  Q1_5_recode = case_when(
    Q1_5_TEXT == "Applied Science" ~ "Division of Sciences",
    Q1_5_TEXT == "Zoology department" ~ "Division of Sciences",
    Q1_5_TEXT == "science communication" ~ "Division of Sciences",
    Q1_5_TEXT == "Psychology" ~ "Division of Sciences",
    Q1_5_TEXT == "Teaching" ~ "Division of Humanities",
    Q1_5_TEXT == "HEDC" ~ "Division of Humanities",
    Q1_5_TEXT == "Social Work" ~ "Division of Humanities",
    Q1_5_TEXT == "National Centre for Peace and Conflict Studies" ~ "Division of Humanities",
    Q1_5_TEXT == "Te Tumu" ~ "Division of Humanities",
    stringr::str_detect(string = Q1_5_TEXT, pattern = "Education") ~ "Division of Humanities", # this finds out what entries contained "Education"
    TRUE ~ Q1_5_TEXT)
)
```



Further tidying for Q22 to remove the text and make a number
```{r}
# a function to pull out the number at the start of a string, when annotation has been added
drop_annotation <- function(column){
  str_split(string = column, pattern = " ") %>% # break up the string into 'words' using a space character
    purrr::map(., 1) %>% # pull out the first 'word' from the list of words
    as.numeric() # convert the 'word' to be an actual number in R 
}

# turn Q22 (and sub questions) into numeric data
# runs drop_annotation() on each column with a column name starting with "Q22_"
student_data_mod <- student_data_mod %>% 
  mutate_at(.vars = vars(starts_with("Q22_")), .funs = drop_annotation) # runs drop_annotation() on each column with a column name starting with "Q22_"
```


plot degree

```{r, fig.width = 6}
ggplot(data = student_data_mod) + geom_bar(mapping = aes(x = Q3, fill = Q2))
```

```{r}
student_data_mod %>% mutate(lib = str_detect(Q9, "lib")) %>%  group_by(lib) %>% tally()
```


How many people are there at each degree stage and what division are they from. This will have a little bit of 'double counting' due to people having multiple divisions. One of the other troubles is that Q1_5 is a free text column so needs cleaning. The cleaning involves combining the two division columns, and then removing the unneeded entries that were fixed. Then we split the division entries out into their own rows and bring the associated data with them 
```{r}
# first grab the columns needed: respondant, division columns (Q1, and Q1_5), and degree (Q2)
division_degree <- student_data_mod %>% select(respondant, Q1, Q1_5_recode, Q2)

division_degree <- division_degree %>% 
  unite(col = division, Q1, Q1_5_recode, sep = ",", remove = FALSE) %>% # cobine the 2 division columns
  mutate(division = str_remove(division, ",NA")) %>% # remove the NA's
  mutate(division = str_remove(division, "Other \\(please state\\),")) # remove the "Other (please state)" entries"
  
division_degree <- division_degree %>% mutate(division = stringr::str_split(division, pattern = ",")) # takes the comma separated entries and splits them to individual entries as a list

division_degree <- division_degree %>% 
  tidyr::unnest(division) %>% # takes the list that was generated and duplicates lines so there is one row corresponding to each list entry
  select(-Q1, -Q1_5_recode) # get rid of the original Q1 columns

division_degree %>% group_by(division, Q2) %>% tally() # create a count for each combination of division and degree that existed
```

